\Large \bf Security Audit of Safeplug ``Tor in a Box''

### 2014-07-13 foci/paper.tex
edited privacy measurement section and fixed figures

\begin{figure*}
  \centering
  \includegraphics[width=0.5\textwidth]{latencygraph}
  \caption{Latency of web requests.}
  \label{fig:latency2}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.5\textwidth]{rangeanddistcocacola}
  \caption{Web request time variation for www.coca-cola.com.}
  \label{fig:boxandwhisker}
\end{figure*}

@@

\section{Privoxy vs. Tor Browser Bundle}
The Safeplug uses two primary technologies: Tor and Privoxy.  The Tor Project has developed the Tor Browser Bundle, which is a free custom browser that uses Tor as well as other protection mechanisms to help preserve a user's privacy.  The Tor Browser Bundle may be a better solution than the Safeplug if it has fewer privacy implications.  The differentiating factor between the Safeplug and the Tor Browser Bundle is the use of Privoxy; in order to determine the effectiveness of the Safeplug in comparison to that of the Tor Browser Bundle, we must measure the value of Privoxy.  We ran a measurement study of the privacy implications of the use of Firefox, Firefox with Privoxy, and the Tor Browser Bundle; our data was collected by running crawls on the Alexa Top 100 sites in each of the specified browsers~\cite{alexa}.  All browser configurations were modified with Pagestats \cite{pagestats} and Cookie Manager+ \cite{cookiemonster} to aggregate information about third party requests, JavaScript objects, flash objects, and third party cookies.  Table \ref{tbb} shows the per page fraction of: third party domains accessed, JavaScript objects received from third parties, flash objects received from third parties, and cookies received from third parties.

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Privacy implications of using Firefox, Privoxy, or the Tor Browser Bundle; the numbers represent the fraction of the corresponding privacy implications per page.}
\label{tbb}
\centering
\small
	\begin{tabular}{| p{1.85cm} | p{1.3cm} | p{1.25cm} | p{.7cm} | p{1cm} |}
	\hline
		Configuration & Third Party Domains & JavaScript & Flash & Cookies \\ \hline
		Plain Firefox	& 0.64 & 0.01 & 0.01 & 0.88 \\ \hline
		Privoxy & 0.72 & 0.00 & 0.01 & 0.84 \\ \hline
		Tor Browser	& 0.58 & 0.01 & 0.00 & 0.00 \\ \hline
	\end{tabular}
\end{table}

It is clear that the Tor Browser Bundle had the fewest privacy implications in most categories. The one category where Privoxy performed better than the Tor Browser Bundle is in the number of JavaScript objects received from third parties; this can be attributed to the fact that our measurements were taken using the default settings for the Tor Browser Bundle, which allows JavaScript~\cite{torproject}.  This is explained on the Tor Project's website; they explain that disabling JavaScript causes some web pages to break, making the browser less user-friendly.  The user has the option to disable JavaScript by simply clicking a button.  This shows that the Tor Browser is a less expensive alternative to the Safeplug, and provides more privacy protections.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{latencygraph}
  \caption{Latency of web requests.}
  \label{fig:latency2}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{rangeanddistcocacola}
  \caption{Web request time variation for www.coca-cola.com.}
  \label{fig:boxandwhisker}
\end{figure}

@@

\section{Privoxy vs. Tor Browser Bundle}
The Safeplug uses two primary technologies: Tor and Privoxy.  The Tor Project has developed the Tor Browser Bundle, which is a free custom browser that uses Tor as well as other protection mechanisms to help preserve a user's privacy.  A differentiating factor between the Safeplug and the Tor Browser Bundle is the use of Privoxy; in order to determine the effectiveness of the Safeplug in comparison to that of the Tor Browser Bundle, we must measure the value of Privoxy.  We ran a privacy study on the use of Firefox, Firefox with Privoxy, and the Tor Browser Bundle; our data was collected by running crawls on the Alexa Top 100 sites in each of the specified browsers~\cite{alexa}.  All browser configurations were modified with Pagestats \cite{pagestats} and Cookie Manager+ \cite{cookiemonster} to aggregate information about third party requests, JavaScript objects, flash objects, and third party cookies.  Because measuring privacy is a difficult task, we measured potential ways for a user's privacy to be compromised.  First, we recorded how many third party domains were accessed per page; this is shown in the second column of Table \ref{tbb}.  The third and fourth columns show the number of JavaScript objects and the number of Flash objects received from third parties per page, respectively.  Lastly, we kept track of the number of third party cookies received per page, and this is seen in the last column.

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Measurements of using Firefox, Privoxy, or the Tor Browser Bundle; the numbers represent the fraction of Third Party Domains accessed per page, Javascript objects received from third parties per page, the number of Flash objects received from third parties per page, and the number of third party cookies received per page.}
\label{tbb}
\centering
\small
	\begin{tabular}{| p{1.85cm} | p{1.3cm} | p{1.25cm} | p{.7cm} | p{1cm} |}
	\hline
		Configuration & Third Party Domains & JavaScript & Flash & Cookies \\ \hline
		Plain Firefox	& 0.64 & 0.01 & 0.01 & 0.88 \\ \hline
		Privoxy & 0.72 & 0.00 & 0.01 & 0.84 \\ \hline
		Tor Browser	& 0.58 & 0.01 & 0.00 & 0.00 \\ \hline
	\end{tabular}
\end{table}

It is clear that the Tor Browser Bundle performed the best in most categories. The one category where Privoxy performed better than the Tor Browser Bundle is in the number of JavaScript objects received from third parties; this can be attributed to the fact that our measurements were taken using the default settings for the Tor Browser Bundle, which allows JavaScript~\cite{torproject}.  This is explained on the Tor Project's website; they explain that disabling JavaScript causes some web pages to break, making the browser less user-friendly.  The user has the option to disable JavaScript by simply clicking a button.  This shows that the Tor Browser is a less expensive alternative to the Safeplug, and provides more privacy protections.
